Methodology for Assessing the State of the Practice for Domain X

### 2020-10-01 StateOfPractice/Methodology/Methodology.tex
Some revisions to the research questions section

Questions from Olu's Research Proposal:
	\begin{enumerate} 
		\item What artifacts are recommended for research software development?
\pmi{remove}
		\item What artifacts do current software projects produce?
\pmi{keep}
\item What information is captured by current software project artifacts?\pmi{keep}
\item What information is necessary to capture for sustainability?\pmi{remove}
\item What information is necessary to capture for productivity?\pmi{remove}
\item What commonalities exist among software artifacts?\pmi{need to review}
\item How can we improve sustainability in research softifacts development practices?\pmi{remove}
\item What are the consequences of technology tools towards sustainability and productivity?\pmi{remove}
\item What are attitudes of research software developers and engineer towards sustainability and productivity with respect to producing softifacts? \pmi{keep}
\item What are the factors that lead to sustainability and productivity?\pmi{remove}
\item What relationships exist between `high rated' software projects and sustainability with respect to research softifacts production? \pmi{remove}
\end{enumerate}

Questions from Overall Research Project folder
\begin{enumerate}
	\item What knowledge is currently captured in the artifacts generated by
	existing open source SCS projects?\pmi{keep}
	\item What principles, processes, methodologies and tools are used by existing open source SCS projects?\pmi{keep}
	\item What are the pain points" for developers working on SCS projects?
	What aspects of the existing processes, methodologies and tools do
	they consider could potentially be improved?\pmi{keep}
	\item For a given software product (softifacts), how can we produce a reasonable measure of the software qualities (correctness, reliability, usability etc.) with a few hours of effort?\pmi{remove}
	\item For a given software product (softifacts), how can we produce a meaningful measure of usability with a few days worth of effort?\pmi{remove}
	\item For a given software product (softifacts), how can we produce a meaningful measure of maintainability (with respect to likely changes) with
	a few days worth of effort?\pmi{remove}
	\item For a given software product (softifacts), how can we produce a meaningful measure of reproducibility/replicability with a few days worth of
	effort?\pmi{remove}
	\item With a reasonable effort and time, how can we compare the productivity between different processes, methodologies and tools?\pmi{remove}
	\item Can a correlation be identified between software projects that use
	best practices for the development process and methodologies and improvement in the qualities of usability, performance and reproducibility/replicability?\pmi{remove}
	\item Ignoring the time and effort required, what knowledge is necessary to
	capture for sustainable SCS? How can this knowledge best be documented in software artifacts?\pmi{remove}
	\item How can Model Driven Engineering and Code Generation be t in the
	development process for SCS to remove as many repetitive, tedious and
	error prone tasks as possible? We will call this the ideal process."\pmi{remove}
	\item How well do existing modelling and code generation tools do at implementing the ideal process"? Candidates for comparison include Drasil
	and Epsilon.\pmi{remove}
	\item How well does a model driven approach to compared to a traditional
	approach for usability, productivity and sustainability?\pmi{remove}
	\item What are the attitudes and preferences of typical users towards an
	implementation of the ideal process"?\pmi{remove}
\end{enumerate}

%In general questions:
%
%\begin{enumerate}
%\item Comparison between domains
%\item How to measure qualities
%\item How does the quality compare for projects with the most resources to %those
%  with the fewest?
%\item What skills/knowledge are needed by future developers?
%\item How can the development process be improved?
%\item What are the common pain points?
%\end{enumerate}
%
%For each domain questions''
%
%\begin{enumerate}
%\item Best examples within the domain
%\item What software artifacts?
%\item What are the pain points?
%\item Any advice on what can be done about the pain points?
%\end{enumerate}
%
%Measure the effort invested and the reward.  Related to sustainability.
%
%Collect the data and see what conclusions follow.  For an individual domain,
%between domains.  The process isn't so much about ranking the software as it is
%about looking at the software closely and see what conclusions arise.  The
%measurements are intended to force scrutiny, from different perspectives.

>>>>

Questions from Olu's Research Proposal:

\begin{enumerate}
\item What artifacts do current software projects produce?  \pmi{keep}
\item What information is captured by current software project
  artifacts? \pmi{keep} \wss{This question probably isn't part of the state of
    the practice exercise, but part of Olu's PhD research.}
\item What are attitudes of research software developers and engineer toward:
\begin{enumerate}
\item sustainability?
\item productivity?
\end{enumerate} \pmi{keep} \wss{What are we hoping to learn from this question?
  This might be a question for Olu, since she currently has the same research question.}
\item For a given domain of research software, what current projects provide the
  best examples of high quality software and documentation? \wss{Reworded
    version of one of Olu's research questions.}
\end{enumerate}

\wss{Rather than focus on sustainability and productivity, should we focus on
  usability and modifiability for the SOP exercise?  Our current questions and
  experiments focus more on these topics.}

Questions from Overall Research Project folder:

\begin{enumerate}
\item What principles, processes, methodologies and tools are used by existing
  open source SCS projects? \pmi{keep}
\item What are the pain points for developers working on SCS projects?  What
  aspects of the existing processes, methodologies and tools do they consider
  could potentially be improved? \pmi{keep}
\end{enumerate}

%In general questions:
%
%\begin{enumerate}
%\item Comparison between domains
%\item How to measure qualities
%\item How does the quality compare for projects with the most resources to %those
%  with the fewest?
%\item What skills/knowledge are needed by future developers?
%\item How can the development process be improved?
%\item What are the common pain points?
%\end{enumerate}
%
%For each domain questions:
%
%\begin{enumerate}
%\item Best examples within the domain
%\item What software artifacts?
%\item What are the pain points?
%\item Any advice on what can be done about the pain points?
%\end{enumerate}
%
%Measure the effort invested and the reward.  Related to sustainability.
%
%Collect the data and see what conclusions follow.  For an individual domain,
%between domains.  The process isn't so much about ranking the software as it is
%about looking at the software closely and see what conclusions arise.  The
%measurements are intended to force scrutiny, from different perspectives.
